Sets

### 2023-10-02 rec06/paper.tex
power set

Intuitively, a set is a collection of elements.
These elements have no internal structures, so you can think of a set as a collection of dots, and the only question that one can ask is ``is $x$ a member of $y$?''
In other words, the language of set theory contains a binary predicate symbol $\in$.
This is known as the \emph{membership relation}.
$x \in y$ means $x$ is an element of $y$.

@@

\begin{lem}
  Every set is a subset of itself.
\end{lem}
\begin{proof}
  Exercise.
\end{proof}

@@

Given a set $w$, there is a \emph{subcollection} of $w$ whose elements satisfy certain property $\varphi$.
\[
  \{ x \in w \mid \varphi(x) \}
\]
We declare that such subcollections are sets.
For example, given the set of all natural numbers $\dN$,
\[
  \{ x \in \dN \mid \mathrm{even}(x) \}
\]
is the subset of all even natural numbers.

@@

\subsection{von Neumann Ordinals}
\label{sec:von-neumann-ordinals}

>>>>

Intuitively, a set is a collection of elements.
These elements have no internal structures, so you can think of a set as a collection of dots, and the only question that one can ask is ``is $x$ a member of $y$?''

The language of set theory contains a binary predicate symbol $\in$.
This is known as the \emph{membership relation}.
$x \in y$ means $x$ is an element of $y$.

@@

\begin{lem}
  Every set is a subset of itself.
  \[
    \forall x.\, x \subseteq x
  \]
\end{lem}
\begin{proof}
  Exercise.
\end{proof}

\begin{eg}\label{eg:subsets}
  \begin{enumerate}
  \item[]
  \item $\varnothing$ has a subset $\varnothing$.
  \item $\{ \varnothing \}$ has subsets $\varnothing$ and $\{ \varnothing \}$.
  \item $\{ a,b \}$ has subsets $\varnothing$, $\{ a \}$, $\{ b \}$, and $\{ a, b \}$.
  \item $\{ a,b,c \}$ has subsets $\varnothing$, $\{ a \}$, $\{ b \}$, $\{ c \}$, $\{ a,b \}$, $\{ a,c \}$, $\{ b,c \}$, and $\{ a,b,c \}$.
  \end{enumerate}
\end{eg}

@@

Given a set $w$, there is a \emph{subcollection} of $w$ whose elements satisfy certain property $\varphi$.
\[
  \{ x \in w \mid \varphi(x) \}
\]
We declare that such subcollections are sets.

\begin{eg}
  \begin{enumerate}
  \item[]
  \item The set of all even natural numbers: $\{ x \in \dN \mid \mathrm{even}(x) \}$.
  \item The set of all odd natural numbers: $\{ x \in \dN \mid \mathrm{odd}(x) \}$.
  \item The set of all integers divisible by 2: $\{ x \in \dZ \mid x \cng 0 \mod 2 \}$.
  \item The set of all real numbers between $0$ and $1$ (inclusive): $\{ x \in \dR \mid 0 \leq x \leq 1 \}$.
  \end{enumerate}
\end{eg}

\subsection{Power Set}
\label{sec:power-set}

In \cref{eg:subsets}, $\{ a,b,c \}$ has subsets $\varnothing$, $\{ a \}$, $\{ b \}$, $\{ c \}$, $\{ a,b \}$, $\{ a,c \}$, $\{ b,c \}$, and $\{ a,b,c \}$.
These subsets form a collection
\[
  \{ \varnothing, \{ a \}, \{ b \}, \{ c \}, \{ a,b \}, \{ a,c \}, \{ b,c \}, \{ a,b,c \} \}
\]
We declare that such a collection is a set.

\begin{defn}
  Let $x$ be a set.
  The \emph{power set} of $x$, denoted $\cP(x)$, is the set of all subsets of $x$.
\end{defn}

\begin{eg}\label{eg:subsets}
  \begin{enumerate}
  \item[]
  \item $\cP(\varnothing) = \{\varnothing\}$.
  \item $\cP(\{ \varnothing \}) = \{\varnothing, \{\varnothing\}\}$.
  \item $\cP(\{\varnothing, \{\varnothing\}\}) = \{ \varnothing, \{\varnothing\}, \{\{\varnothing\}\}, \{\varnothing, \{\varnothing\}\} \}$.
  \item $\cP(\{ a,b,c \}) = \{ \varnothing, \{ a \}, \{ b \}, \{ c \}, \{ a,b \}, \{ a,c \}, \{ b,c \}, \{ a,b,c \} \}$.
  \end{enumerate}
\end{eg}

\begin{thm}[Cantor's Theorem]
  For any set $x$, there is no surjective function $f : x \to \cP(x)$.
\end{thm}

@@
